Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-11-12 manuscript/manuscript.tex
Fix editor's remark 6

We define an external computation point $P(r, \phi, \lambda)$ in a geocentric spherical
coordinate system at a radius $r$, geocentric latitude $\phi$, and longitude $\lambda$
where the gravitational fields are going to be calculated.
The first and second derivatives of the gravitational potential are taken with
respect to the local north-oriented Cartesian coordinate system of $P$
(Fig.~\ref{fig:tesseroid}).
\citet{Grombein2013} provide efficient formulations for the volume integrals of the
gravitational potential and its first and second derivatives of a tesseroid with
homogeneous density.
Here, we will assume that the tesseroid has a density varying with $r$ according to an
arbitrary function $\rho(r)$.
Thus, the integrals for the gravitational fields are slightly modified to

>>>>

We define an external computation point $P(r, \phi, \lambda)$ in a geocentric spherical
coordinate system at a radius $r$, geocentric latitude $\phi$, and longitude $\lambda$
where the gravitational fields are going to be calculated.
The first- and second-order derivatives of the gravitational potential are taken with
respect to the local north-oriented Cartesian coordinate system of $P$
(Fig.~\ref{fig:tesseroid}).
\citet{Grombein2013} provide efficient formulations for the volume integrals of the
gravitational potential and its first- and second-order derivatives of a tesseroid with
homogeneous density.
Here, we will assume that the tesseroid has a density varying with $r$ according to an
arbitrary function $\rho(r)$.
Thus, the integrals for the gravitational fields are slightly modified to
